### 2023-02-15 paper-thesis/chapters/11-variable-capture.tex
Add chapter transitions
Meeting results

An example term where this problem occurs is the following: What is the type of this expression (a polymorphic identity function)?
\begin{lstlisting}
\T : Type. \T : T. T
\end{lstlisting}
The implementation so far would tell you it is \verb|T : Type -> T : T -> T|. Given the scoping rules of the language, that is equivalent to \verb|T : Type -> x : T -> x|. However, the correct answer would be \verb|T : Type -> x : T -> T|. There is no way of expressing this type without renaming a variable.

@@

>>>>

An example term where this problem occurs is the following: What is the type of this expression (a polymorphic identity function)?
\begin{lstlisting}
\T : Type. \T : T. T
\end{lstlisting}
The implementation so far would tell you it is \verb|T : Type -> T : T -> T| \todo{why is this wrong}. Given the scoping rules of the language, that is equivalent to \verb|T : Type -> x : T -> x|. However, the correct answer would be \verb|T : Type -> x : T -> T|. There is no way of expressing this type without renaming a variable.

@@

We have now solved the problem of variable capture. In chapter \ref{chap:bools}, we explain how to extend the language further, by extending it with booleans. Then, from chapter \ref{ch:inference} onward we use this method to extend the language with various features.
